DNSKEY Management

### 2012-12-04 paper/paper.tex
oups, deleted some stuff, putting it back.

\begin{itemize}
\item the registry;
\item the registrant;
\item the registrar.
\end{itemize}

The registries are the entities serving the records for a zone. For example, Switch is the registry for the \verb|ch.| zone. Registrants, on their side, are the entities willing to obtain a certain domain: the registrant of \verb|epfl.ch| is the school in itself, for example.

@@

In Switzerland, for example, Switch plays both the roles of the registry and a registrar: other registrars also exist but one can purchase a domain name directly from Switch. Registries will generally delegate part or whole of the namespace registration managing to registrars.

Registrants are also free to play the registry and registrant roles for their own sub-domains: groups, laboratories and associations within EPFL will obtain an \verb|epfl.ch| sub-domain, like the LACAL and it's \verb|lacal.epfl.ch| subdomain, for example.

The entities behind the three R's are the exact same whether DNSSEC is used or not, but DNSSEC modifies the relations among them: e.g., DNSKEY updates will now also require communication between the three R's, even if no practical information like IP addresses or billing data actually changed.

\subsection{Signing a zone}
Whenever an entity wishes to sign its zone, it should ideally turn to its already signed parent zone, in order to create a continuous trust chain, as said parent will then serve a DS record containing the child zone's key signature.

@@

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant for such jitter: typically, if the \verb|epfl.ch| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch|'s DNS servers will appear as illegitimate whereas they perfectly are.
\subsection{Disabling DNSSEC}

>>>>

\begin{itemize}
\item a registry;
\item a registrant;
\item a registrar.
\end{itemize}

The registries are the entities serving the records for a zone. For example, Switch is the registry for the \verb|ch.| zone. Registrants, on their side, are the entities willing to obtain a certain domain: the registrant of \verb|epfl.ch| is the school in itself (its IT-department to be precise \footnote{As a \emph{whois} query on the epfl.ch domain will show you.}), for example.

@@

In Switzerland, for example, Switch plays both the roles of the registry and a registrar: other registrars also exist but one can purchase a domain name directly from Switch. Registries will generally delegate part or whole of the namespace registration managing to registrars\footnote{For example, one can also buy a .ch domain from \url{http://gandi.net}}

Registrants are also free to play the registry and registrar roles for their own sub-domains: groups, laboratories and associations within EPFL may apply for an \verb|epfl.ch| sub-domain, like the LACAL and it's \verb|lacal.epfl.ch| subdomain, for example.

The entities behind the three R's are the exact same whether DNSSEC is used or not, but DNSSEC modifies the relations among them: e.g., DNSKEY updates will now also require communication between the three R's, even if no practical information like IP addresses or billing data was actually updated.

\subsection{Signing a zone}
Whenever an entity wishes to sign its zone, it should ideally turn to its already signed parent zone, in order to create a continuous trust chain.
Said parent should then serve a DS record containing the child zone's key signature.

@@

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant for such jitter: typically, if the \verb|epfl.ch| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch|'s DNS servers will appear as illegitimate whereas they perfectly are.

\subsection{Disabling DNSSEC}
